On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-08 MS.tex
Editing in Results part: Comparison RGR AGR Change Fig 3 and 4: "n" were overlapping CI

The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass. Overall, the model fits did not improve when information about growth measurement (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig. \ref{fig:fig4}), thus supporting this claim. For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with absolute versus relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was negative and shifted to non-significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4} d). For wood density, some differences were observed between studies reporting relative and absolute growth rates: in particular, the correlation at juvenile stage shifted from negative with relative growth rate to non-significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). There may be several reasons for this difference, however, we note that the only available correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike most other studies, they used wood density values estimated on adult plants together with growth data taken from seedlings. This suggest possible confounding between the type of growth measurement and origin of the trait data.

@@

\clearpage
\begin{table}[h!]
\centering
\caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
  \hline
  & Quality criteria & Check & How and where is it addressed?\\
  \hline
  1.& Reporting full details of bibliographic searches & yes  & Complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
  2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''. A full list of all articles evaluated is available in the Appendix \ref{app:literature-list}.\\
  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See ``Material and Methods'' for details.\\
 4.& Specifying meta-analytical model & yes & We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect. See ``Material and Methods'' for details. Results are shown in Fig. \ref{fig:fig3} \& \ref{fig:fig4}.\\
 5.& Quantifying heterogeneity in effect sizes &  yes & We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
 6.& Exploring causes of heterogeneity & yes &  We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
 7.& Multifactorial analysis of explanatory variable  & yes & We check whether several other explanatory moderators (i.e. growth measurement, experiment type or growth form) are consistently the strongest predictors of the data. We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See in Figs \ref{fig:figA6}.\\
  8.& Testing for publication bias &  yes & We used several methods (i.e. funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number). See Appendix \ref{app:supp_info_analyses} for details.\\
  9.& Sensitivity analysis &  yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig4} \& \ref{fig:figA5}.\\
  10.& Exploring temporal changes in effect size &  yes & See Appendix \ref{app:supp_info_analyses} for details.\\
  11.& Controlling for phylogeny &  no &  It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
  12.& Specifying the software used & yes & See sections in ``Material and Methods'' and ``Availability of code and data''.\\
 13.& Providing reference list of primary studies included in the analysis &  yes & All articles from which data were extracted are cited in the paper.\\
  14.& Providing the data set used for meta-analysis  & yes & A copy of the data set is available. See ``Availability of code and data'' for details.\\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}

>>>>

The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass. Overall, the model fits did not improve when information about growth measurement (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig. \ref{fig:fig4}), thus supporting this claim. For all traits, effect sizes were non significantly different between relative growth rate and absolute growth rate when both measurements were available (e.g. CIs overlapping between relative and abolute growth rates for each stage, Fig. \ref{fig:fig4}). Effect sizes measured with a same number of observations for relative and absolute growth rate were generally very consistent (i.e. Hmax and wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with absolute versus relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was negative and shifted to positive (but non-significant; CI included zero, Fig \ref{fig:fig4}d) with absolute growth rate. While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4} d). For wood density, some differences were observed between studies reporting relative and absolute growth rates: in particular, the correlation at seedling stage shifted from negative with relative growth rate to positive (but non-significant; CI included zero, Fig. \ref{fig:fig4}b) with absolute growth rate. There may be several reasons for this difference, however, we note that the only available correlation coefficients recorded for absolute growth rate at seedling stage came from \citet{Augspurger:1984ct}, and unlike most other studies, they used wood density values estimated on adult plants together with growth data taken from seedlings. This suggests possible confounding between the type of growth measurement and origin of the trait data.

@@

\clearpage
\begin{table}[h!]
\centering
\caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
{\footnotesize
\vspace{0.5cm}
\begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
  \hline
  & Quality criteria & Check & How and where is it addressed?\\
  \hline
  1.& Reporting full details of bibliographic searches & yes  & Complete details of bibliographic searches (i.e. electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
  2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''. A full list of all articles evaluated is available in the Appendix \ref{app:literature-list}.\\
  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See ``Material and Methods'' for details.\\
 4.& Specifying meta-analytical model & yes & We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect. See ``Material and Methods'' for details. Results are shown in Fig. \ref{fig:fig3} \& \ref{fig:fig4}.\\
 5.& Quantifying heterogeneity in effect sizes &  yes & We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
 6.& Exploring causes of heterogeneity & yes &  We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
 7.& Multifactorial analysis of explanatory variable  & yes & We check whether several other explanatory moderators (i.e. growth measurement, experiment type or growth form) are consistently the strongest predictors of the data. We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset. See in Figs \ref{fig:figA6}.\\
  8.& Testing for publication bias &  yes & We used several methods (i.e. funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number). See Appendix \ref{app:supp_info_analyses} for details.\\
  9.& Sensitivity analysis &  yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig3} \& \ref{fig:figA5}.\\
  10.& Exploring temporal changes in effect size &  yes & See Appendix \ref{app:supp_info_analyses} for details.\\
  11.& Controlling for phylogeny &  no &  It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
  12.& Specifying the software used & yes & See sections in ``Material and Methods'' and ``Availability of code and data''.\\
 13.& Providing reference list of primary studies included in the analysis &  yes & All articles from which data were extracted are cited in the paper.\\
  14.& Providing the data set used for meta-analysis  & yes & A copy of the data set is available. See ``Availability of code and data'' for details.\\
   \hline
\end{tabular}
}
\label{tab:meta}
\end{table}
